---
title: "A Model to Predict Chances of Matching into Obstetrics and Gynecology Residency"
author: "Tyler M. Muffly, MD"
date: "Department of Obstetrics and Gynecology, Denver Health, Denver, CO"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    self_contained: true
    code_folding: show
    dev: svg
    df_print: paged
    theme: journal
  pdf_document:
    pandoc_args:
    - --wrap=none
    - --top-level-division=chapter
    df_print: paged
    fig_caption: yes
    #keep_tex: no
    latex_engine: xelatex
  word_document:
    toc_depth: '2'
fontsize: 12pt
geometry: margin=1in
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[R]{Muffly et al.}
- \usepackage{lineno}
- \linenumbers
fontfamily: mathpazo
spacing: double
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---
*Tyler M. Muffly, Merdith Alston, Jill Liss, Georg Kropat, Janet Corral, Christine Raffaelli, J. Eric Jelovsek*
*Authorship order will be determined by the amount of work done.*
- name: Tyler M. Muffly, MD
  affiliation: Denver Health
- name: Meredith Alston, MD
  affiliation: Denver Health
- name: Jill Liss
  affiliation: University of Colorado
- name: Michael Courtois, MS
  affiliation: Denver Health
- name: Georg Kropat, PhD
  affiliation: R & D Services
- name: Janet Corall, PhD
  affiliation: University of Colorado
- name: Christine Raffaelli
  affiliation: University of Colorado
- name: J. Eric Jelovsek
  affiliation: Duke University

*Objective:  *
*We sought to construct and validate a model that predict a medical student's chances of matching into an obstetrics and gynecology residency.*

The Electronic Residency Application Service (ERAS) is a centralized solution to the medical residency application and documents distribution process. The data source to be used for the project is the Electronic Residency Application Service data that was in discrete fields in the application.  No hand-searching of data was done. The data was exported from the ERAS Program Director Work Station under the Archives menu.The data is collected by the University of Colorado OBGYN residency that has both a categorical and a preliminary position.  Medical students who applied to the preliminary position were considered to be unmatched. The data set of years 2015, 2016, 2017, and 2018 applicants to the University of Colorado OBGYN residency. The data is contained in a data frame called 'all_data'. In advance, we might anticipate that USMLE Step 1 Score and US or Canadian Applicant will be key predictors.  Match Status is the dependent Variable and shows the medical students who applied to the OBGYN residency. 

# Codebook
A codebook is a technical description of the data that was collected for a particular purpose. It describes how the data are arranged in the computer file or files, what the various numbers and letters mean, and any special instructions on how to use the data properly.

* Predictors under consideration:
1. `all_data$white_non_white` - Dichotomoized from ethnicity fields in ERAS data, 2 level categorical
2. `all_data$Age` - Age at the time of the match, numerical variable
3. `all_data$Year` - Year of participation in the match, 4 level categorical.  Will not have data of year in future so to remove.  
4. `all_data$Gender` - Male or Female, 2 level categorical
5. `all_data$Couples_Match` - PArticipating in the couples match? 2 level categorical.  We are unsure if there are any couples who are both matching into OBGYN.  
6. `all_data$US_or_Canadian_Applicant` - Are they a US/Canadian Senior "Yes" or an International medical graduate "No"?  , 2 level categorical 
7. `all_data$Medical_Education_or_Training_Interrupted` - Taking breaks, 2 level categorical
8. `all_data$Alpha_Omega_Alpha` - Membership in AOA, 3 level categorical.  Yes means elected in their junior year or elections are early.  Could combine with Sigma Sigma Phi?  Passing minimum score is 194 and theoretical maximum score is 300.  
9. `all_data$Military_Service_Obligation`
10. `all_data$USMLE_Step_1_Score` - I did not use Step 2 score because most students will not have those numbers at the time they apply, numerical variable
11. `all_data$Count_of_Poster_Presentation` - numerical variable
12. `all_data$Count_of_Oral_Presentation` - numerical variable
13. `all_data$Count_of_Articles_Abstracts` - numerical variable
14. `all_data$Count_of_Peer_Reviewed_Book_Chapter` - numerical variable
15. `all_data$Count_of_Other_than_Published` - numerical variable
16. `all_data$Visa_Sponsorship_Needed` - numerical variable
17. `all_data$Medical_Degree` - Allopathic versus Osteopathic medical school education, 2 level categorical

This data was cleaned in a separate R script with the help of exploratory.io.  

Packrat is in use to control package versions and a packrat.lock file is posted to my github repository.  This will allow for easier reproducibility.  Packrat records the exact package versions you depend on, and ensures those exact versions are the ones that get installed wherever you go.  We can also control the environment by deploying the project inside a Docker container as needed.  The project was created in R version 3.6.1 and run inside RStudio 1.2.5019.  Session info is present at the bottom of the script.  

```{r}
#### #### #### #### #### #### #### #### #### #### #### #### #### #### #### #### 
#####  Functions for nomogram
#### #### #### #### #### #### #### #### #### #### #### #### #### #### #### #### 
create_plot_num <- 
  function(data) {
    print("Function Sanity Check: Plot Numeric Features")
    funModeling::plot_num(data, path_out = results_folder)
  } 

create_plot_cross_plot <- 
  function(data) {
    print("Function Sanity Check: Cross Plot Features")
    funModeling::cross_plot(data, 
                            input=(colnames(data)), 
                            target="Match_Status", 
                            path_out = results_folder,
                            auto_binning = TRUE)
  } #, auto_binning = FALSE, #Export results
#For numerical variables, cross_plot has by default the auto_binning=T, which automatically calls the equal_freq function with n_bins=10 (or the closest number).

create_profiling_num <- 
  function(data) {
    print("Function Sanity Check: Plot Numeric Features")
    funModeling::profiling_num(data)
  }

#https://www.kaggle.com/pjmcintyre/titanic-first-kernel#final-checks
tm_nomogram_prep <- function(df){  #signature of the function
  set.seed(1978)                  #body of the function
  print("Function Sanity Check: Creation of Nomogram")
  test <- rms::nomogram(df,
                #lp.at = seq(-3,4,by=0.5),
                fun = plogis,
                fun.at = c(0.001, 0.01, 0.05, seq(0.2, 0.8, by = 0.2), 0.95, 0.99, 0.999),
                funlabel = "Chance of Matching in OBGYN",
                lp =FALSE,
                #conf.int = c(0.1,0.7),
                abbrev = F,
                minlength = 9)
  
  tm_plot <- plot(test, lplabel="Linear Predictor",
       cex.sub = 0.3, cex.axis=0.4, cex.main=1, cex.lab=0.2, ps=10, xfrac=1,
       col.conf=c('red','green'),
       conf.space=c(0.1,0.5),
       label.every=1,
       col.grid = gray(c(0.8, 0.95)),
       which="Match_Status")
  return(tm_plot)
  }

tm_rpart_plot = function(df){
  print("Function Sanity Check: Plot Decision Trees using package rpart with Leaves")
  tm_rpart_plot_leaves <- rpart.plot::rpart.plot(df, yesno = 2, type = 5, extra = +100, fallen.leaves = TRUE, varlen = 0, faclen = 0, roundint = TRUE, clip.facs = TRUE, shadow.col = "gray", main = "Tree Model of Medical Students Matching into OBGYN Residency\n(Matched or Unmatched)", box.palette = c("red", "green"))  
  tm_fancy_rpart <- fancyRpartPlot(df)
  return(c(tm_rpart_plot_leaves, tm_fancy_rpart))
  }

# Draws a nice table one plot
tm_arsenal_table = function(df, by){
  print("Function Sanity Check: Create Arsenal Table using arsenal package")
  table_variable_within_function <- arsenal::tableby(by ~ .,
                 data=df, control = tableby.control(test = TRUE,
                                                                total = F,
                                                                digits = 1L,
                                                                digits.p = 2L,
                                                                digits.count = 0L,
                                                                numeric.simplify = F,
                                                                numeric.stats =
                                                                  c("median",
                                                                    "q1q3"),
                                                                cat.stats =
                                                                  c("Nmiss",
                                                                    "countpct"),
                                                                stats.labels = list(Nmiss = "N Missing",
                                                                                    Nmiss2 ="N Missing",
                                                                                    meansd = "Mean (SD)",
                                                                                    medianrange = "Median (Range)",
                                                                                    median ="Median",
                                                                                    medianq1q3 = "Median (Q1, Q3)",
                                                                                    q1q3 = "Q1, Q3",
                                                                                    iqr = "IQR",
                                                                                    range = "Range",
                                                                                    countpct = "Count (Pct)",
                                                                                    Nevents = "Events",
                                                                                    medSurv ="Median Survival",
                                                                                    medTime = "Median Follow-Up")))
  final <- summary(table_variable_within_function,
          text=T,
          title = 'Table: Applicant Descriptive Variables by Matched or Did Not Match from 2015 to 2018',
          labelTranslations = mylabels, #Seen in additional functions file
          pfootnote=TRUE)
  return(final)
}

#Draws a nice plot of the variable strengths using ANOVA.  
tm_chart_strength_of_variables <- function(df) {
  print("Function Sanity Check: Plotting ANOVA dataframe for variable strength")
  plot <- plot(anova(df), cex=1, cex.lab=1.3, cex.axis = 0.9)
  return(plot)
}

#Helpful plot of variable importance for variable selection
tm_variable_importance = function(df) {
  print("Function Sanity Check: Evaluate Variable Importance")
  rf_imp <- varImp(df, scale = FALSE)
  rf_imp <- rf_imp$importance
  rf_gini <- data.frame(Variables = row.names(rf_imp), MeanDecreaseGini = rf_imp$Overall)
  
  rf_plot <- ggplot(rf_gini, aes(x=reorder(Variables, MeanDecreaseGini), y=MeanDecreaseGini, fill=MeanDecreaseGini)) +
    geom_bar(stat='identity') + coord_flip() + theme(legend.position="none") + labs(x="") +
    ggtitle('Variable Importance Random Forest') + theme(plot.title = element_text(hjust = 0.5))
  return(rf_plot)
}

calc_metrics <- function(model, new_data, truth) {
  truth_expr <- enquo(truth)
  
  suppressWarnings({
    model %>%
      stats::predict(new_data = new_data) %>%
      bind_cols(new_data %>% select(!! truth_expr)) %>%
      yardstick::metrics(truth = !! truth_expr, 
              estimate = .pred) %>%
      dplyr::select(-.estimator) %>%
      tidyr::spread(.metric, .estimate)
  })
  
}

#Tidymodels feature plots
box_fun_plot = function(data, x, y) {
  ggplot2::ggplot(data = data, ggplot2::aes(x = .data[[x]],
                          y = .data[[y]],
                          fill = .data[[x]])) +
    geom_boxplot() +
    labs(title = y,
         x = x,
         y = y) +
    theme(
      legend.position = "none"
    )
}

density_fun_plot = function(data, x, y) {
  ggplot(data = data, aes(x = .data[[y]],
                          fill = .data[[x]])) +
    geom_density(alpha = 0.7) +
    labs(title = y,
         x = y) +
    theme(
      legend.position = "none"
    )
}

#Recipe function - First, I create a recipe where I define the transformations I want to apply to my data. In this case I create a simple recipe to change all character variables to factors.
#https://ryjohnson09.netlify.com/post/caret-and-tidymodels/

#The order in which you infer, center, scale, etc does matter (see this post).

# 1) Impute
# 2) Individual transformations for skewness and other issues
# 3) Discretize (if needed and if you have no other choice)
# 4) Create dummy variables
# 5) Create interactions
# 6) Normalization steps (center, scale, range, etc)
# 7) Multivariate transformation (e.g. PCA, spatial sign, etc)

recipe_simple <- function(dataset) {
  recipe(Match_Status ~ ., data = dataset) %>%
  recipes::step_string2factor(all_nominal(), -all_outcomes()) %>%
    add_role(Match_Status, new_role = "outcome") %>% 
    add_role(starts_with("Count_of_"), new_role = "predictor") %>% 
    add_role(white_non_white, Age, Gender, Couples_Match, US_or_Canadian_Applicant, Medical_Education_Interrupted, Alpha_Omega_Alpha, Military_Service_Obligation, USMLE_Step_1_Score, Visa_Sponsorship_Needed, Medical_Degree, new_role = "predictor") %>%
  recipes::step_corr(all_numeric(), method = "pearson", threshold = 0.9)
  }   #Cool looks for correlation
    # Add dummy variables for "class" variables
    #recipes::step_dummy(all_nominal(), -all_outcomes(), one_hot = TRUE) %>%  #Deal with categories
    # Center and Scale
    # recipes::step_center(all_predictors()) %>% 
    # recipes::step_scale(all_predictors())


#Now I need to create a function that contains my model that can be iterated over each split of the data. I also want a function that will make predictions using said model.
fit_mod_func <- function(split, spec){
  print("Function Sanity Check: Function to fit her model using parsnip package")
  parsnip::fit(object = spec,
      formula = Match_Status ~ .,
      data = rsample::analysis(split))
}

predict_func <- function(split, model){
  print("Function Sanity Check: Prediction Function")
  # Extract the assessment data
  assess <- rsample::assessment(split)
  # Make prediction
  pred <- stats::predict(model, new_data = assess)
  dplyr::as_tibble(cbind(assess, pred[[1]]))
}

# Will calculate accuracy of classification
#perf_metrics <- yardstick::metric_set(accuracy)

# Create a function that will take the prediction and compare to truth
rf_metrics <- function(pred_df){
  print("Function Sanity Check: Compare the truth to the predictions")
  perf_metrics(
    pred_df,
    truth = Match_Status,
    estimate = res # res is the column name for the predictions
  )
}

#https://tidymodels.github.io/rsample/articles/Working_with_rsets.html
tm_holdout_results <- function(splits, ...) {
  # Fit the model to the 90%
  mod <- glm(..., data = analysis(splits), family = binomial)
  # Save the 10%
  holdout <- assessment(splits)
  # `augment` will save the predictions with the holdout data set
  res <- broom::augment(mod, newdata = holdout)
  # Class predictions on the assessment set from class probs
  lvls <- levels(holdout$Match_Status)
  predictions <- factor(ifelse(res$.fitted > 0, lvls[2], lvls[1]),
                        levels = lvls)
  # Calculate whether the prediction was correct
  res$correct <- predictions == holdout$Match_Status
  # Return the assessment data set with the additional columns
  res
}

tm_confusion_matrix_graph <- function (model_name, label) {  #label should be in quotation marks
  print("Function Sanity Check: Create Confusino Matrix Graphs")
model_name %>%  #Plug in the model using the training data
  stats::predict(new_data = test_baked) %>%  #Predict the test_data with the new model
  bind_cols(test_baked) %>%
  conf_mat(Match_Status, .pred_class) %>%
  purrr::pluck(1) %>%
  tibble::as_tibble() %>%
  ggplot2::ggplot(aes(Prediction, Truth, alpha = n)) +  
  ggplot2::geom_tile(show.legend = FALSE) +
  ggplot2::geom_text(aes(label = n), colour = "white", alpha = 1, size = 8) +
  labs(
    title = paste('Confusion matrix using:', label, sep = " ")) }

# HR 201: PREDICTING EMPLOYEE ATTRITION WITH H2O AND LIME ----
# CHAPTER 4: H2O MODELING ----
# Extracts and H2O model name by a position so can more easily use h2o.getModel()
extract_h2o_model_name_by_position <- function(h2o_leaderboard, n = 1, verbose = T) {
  print("Function Sanity Check: Extracts H2O model name as a position")
  
  model_name <- h2o_leaderboard %>%
    as.tibble() %>%
    dplyr::slice(n) %>%
    pull(model_id)
  
  if (verbose) message(model_name)
  
  return(model_name)
  
}


# Visualize the H2O leaderboard to help with model selection
plot_h2o_leaderboard <- function(h2o_leaderboard, order_by = c("auc", "logloss"), 
                                 n_max = 20, size = 4, include_lbl = TRUE) {
  print("Function Sanity Check: H2O leaderboard visualization")
  # Setup inputs
  order_by <- tolower(order_by[[1]])
  
  leaderboard_tbl <- h2o_leaderboard %>%
    as.tibble() %>%
    dplyr::mutate(model_type = str_split(model_id, "_", simplify = T) %>% .[,1]) %>%
    rownames_to_column(var = "rowname") %>%
    dplyr::mutate(model_id = paste0(rowname, ". ", as.character(model_id)) %>% as.factor())
  
  # Transformation
  if (order_by == "auc") {
    
    data_transformed_tbl <- leaderboard_tbl %>%
      dplyr::slice(1:n_max) %>%
      dplyr::mutate(
        model_id   = as_factor(model_id) %>% reorder(auc),
        model_type = as.factor(model_type)
      ) %>%
      tidyr::gather(key = key, value = value, 
             -c(model_id, model_type, rowname), factor_key = T)
    
  } else if (order_by == "logloss") {
    
    data_transformed_tbl <- leaderboard_tbl %>%
      dplyr::slice(1:n_max) %>%
      dplyr::mutate(
        model_id   = as_factor(model_id) %>% reorder(logloss) %>% fct_rev(),
        model_type = as.factor(model_type)
      ) %>%
      tidyr::gather(key = key, value = value, -c(model_id, model_type, rowname), factor_key = T)
    
  } else {
    stop(paste0("order_by = '", order_by, "' is not a permitted option."))
  }
  
  # Visualization
  print("Function Sanity Check: Creating Visualization")
  g <- data_transformed_tbl %>%
    ggplot(aes(value, model_id, color = model_type)) +
    geom_point(size = size) +
    facet_wrap(~ key, scales = "free_x") +
    #tidyquant::theme_tq() +
    scale_color_tq() +
    labs(title = "Leaderboard Metrics",
         subtitle = paste0("Ordered by: ", toupper(order_by)),
         y = "Model Postion, Model ID", x = "")
  
  if (include_lbl) g <- g + geom_label(aes(label = round(value, 2), hjust = "inward"))
  
  return(g)
  
}


# Convert a leaderboard into a Performance Diagnostic Dashboard
# containing an ROC Plot, Precision vs Recall Plot, Gain Plot, and Lift Plot
plot_h2o_performance <- function(h2o_leaderboard, newdata, order_by = c("auc", "logloss"),
                                 max_models = 3, size = 1.5) {
  print("Function Sanity Check: Plot H2O performance")
  # Inputs
  
  leaderboard_tbl <- h2o_leaderboard %>%
    as.tibble() %>%
    dplyr::slice(1:max_models)
  
  newdata_tbl <- newdata %>%
    as.tibble()
  
  order_by <- tolower(order_by[[1]])
  order_by_expr <- rlang::sym(order_by)
  
  h2o.no_progress()
  
  # 1. Model metrics
  print("Function Sanity Check: Check Model Performance Metrics")
  get_model_performance_metrics <- function(model_id, test_tbl) {
    
    model_h2o <- h2o.getModel(model_id)
    perf_h2o  <- h2o.performance(model_h2o, newdata = as.h2o(test_tbl))
    
    perf_h2o %>%
      h2o.metric() %>%
      as.tibble() %>%
      select(threshold, tpr, fpr, precision, recall)
    
  }
  
  model_metrics_tbl <- leaderboard_tbl %>%
    dplyr::mutate(metrics = map(model_id, get_model_performance_metrics, newdata_tbl)) %>%
    unnest() %>%
    dplyr::mutate(
      model_id = as_factor(model_id) %>% 
        fct_reorder(!! order_by_expr, .desc = ifelse(order_by == "auc", TRUE, FALSE)),
      auc  = auc %>% 
        round(3) %>% 
        as.character() %>% 
        as_factor() %>% 
        fct_reorder(as.numeric(model_id)),
      logloss = logloss %>% 
        round(4) %>% 
        as.character() %>% 
        as_factor() %>% 
        fct_reorder(as.numeric(model_id))
    )
  
  
  # 1A. ROC Plot
  
  p1 <- model_metrics_tbl %>%
    ggplot(aes_string("fpr", "tpr", color = "model_id", linetype = order_by)) +
    geom_line(size = size) +
    #tidyquant::theme_tq() +
    scale_color_tq() +
    labs(title = "ROC", x = "FPR", y = "TPR") +
    theme(legend.direction = "vertical")
  
  # 1B. Precision vs Recall
  
  p2 <- model_metrics_tbl %>%
    ggplot(aes_string("recall", "precision", color = "model_id", linetype = order_by)) +
    geom_line(size = size) +
    #tidyquant::theme_tq() +
    scale_color_tq() +
    labs(title = "Precision Vs Recall", x = "Recall", y = "Precision") +
    theme(legend.position = "none")
  
  
  # 2. Gain / Lift
  
  get_gain_lift <- function(model_id, test_tbl) {
    
    model_h2o <- h2o.getModel(model_id)
    perf_h2o  <- h2o.performance(model_h2o, newdata = as.h2o(test_tbl)) 
    
    perf_h2o %>%
      h2o.gainsLift() %>%
      as.tibble() %>%
      select(group, cumulative_data_fraction, cumulative_capture_rate, cumulative_lift)
    
  }
  
  gain_lift_tbl <- leaderboard_tbl %>%
    dplyr::mutate(metrics = map(model_id, get_gain_lift, newdata_tbl)) %>%
    unnest() %>%
    dplyr::mutate(
      model_id = as_factor(model_id) %>% 
        fct_reorder(!! order_by_expr, .desc = ifelse(order_by == "auc", TRUE, FALSE)),
      auc  = auc %>% 
        round(3) %>% 
        as.character() %>% 
        as_factor() %>% 
        fct_reorder(as.numeric(model_id)),
      logloss = logloss %>% 
        round(4) %>% 
        as.character() %>% 
        as_factor() %>% 
        fct_reorder(as.numeric(model_id))
    ) %>%
    rename(
      gain = cumulative_capture_rate,
      lift = cumulative_lift
    ) 
  
  # 2A. Gain Plot
  
  p3 <- gain_lift_tbl %>%
    ggplot(aes_string("cumulative_data_fraction", "gain", 
                      color = "model_id", linetype = order_by)) +
    geom_line(size = size) +
    geom_segment(x = 0, y = 0, xend = 1, yend = 1, 
                 color = "black", size = size) +
    #tidyquant::theme_tq() +
    scale_color_tq() +
    expand_limits(x = c(0, 1), y = c(0, 1)) +
    labs(title = "Gain",
         x = "Cumulative Data Fraction", y = "Gain") +
    theme(legend.position = "none")
  
  # 2B. Lift Plot
  
  p4 <- gain_lift_tbl %>%
    ggplot(aes_string("cumulative_data_fraction", "lift", 
                      color = "model_id", linetype = order_by)) +
    geom_line(size = size) +
    geom_segment(x = 0, y = 1, xend = 1, yend = 1, 
                 color = "black", size = size) +
    #tidyquant::theme_tq() +
    scale_color_tq() +
    expand_limits(x = c(0, 1), y = c(0, 1)) +
    labs(title = "Lift",
         x = "Cumulative Data Fraction", y = "Lift") +
    theme(legend.position = "none")
  
  
  # Combine using cowplot
  p_legend <- get_legend(p1)
  p1 <- p1 + theme(legend.position = "none")
  
  p <- cowplot::plot_grid(p1, p2, p3, p4, ncol = 2) 
  
  p_title <- ggdraw() + 
    draw_label("H2O Model Metrics", size = 18, fontface = "bold", 
               colour = palette_light()[[1]])
  
  p_subtitle <- ggdraw() + 
    draw_label(glue("Ordered by {toupper(order_by)}"), size = 10,  
               colour = palette_light()[[1]])
  
  ret <- plot_grid(p_title, p_subtitle, p, p_legend, 
                   ncol = 1, rel_heights = c(0.05, 0.05, 1, 0.05 * max_models))
  
  h2o.show_progress()
  
  return(ret)
  
}

# Precision vs Recall
load_model_performance_metrics <- function(path, test_tbl) {
  print("Function Sanity Check: Load Model Performance Metrics")
  model_h2o <- h2o.loadModel(path)
  perf_h2o  <- h2o.performance(model_h2o, newdata = as.h2o(test_tbl)) 
  
  perf_h2o %>%
    h2o.metric() %>%
    as.tibble() %>%
    mutate(auc = h2o.auc(perf_h2o)) %>%
    select(tpr, fpr, auc, precision, recall)
}


plot_features_tq <- function(explanation, ncol) {
  print("Function Sanity Check: Plot Features using the TQ theme")
  data_transformed <- explanation %>%
    as.tibble() %>%
    mutate(
      feature_desc = as_factor(feature_desc) %>% 
        fct_reorder(abs(feature_weight), .desc = FALSE),
      key     = ifelse(feature_weight > 0, "Supports", "Contradicts") %>% 
        fct_relevel("Supports"),
      case_text    = glue("Case: {case}"),
      label_text   = glue("Label: {label}"),
      prob_text    = glue("Probability: {round(label_prob, 2)}"),
      r2_text      = glue("Explanation Fit: {model_r2 %>% round(2)}")
    ) %>%
    select(feature_desc, feature_weight, key, case_text:r2_text)
  
  
  data_transformed %>%
    ggplot(aes(feature_desc, feature_weight, fill = key)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    #theme_tq() +
    scale_fill_tq() +
    labs(y = "Weight", x = "Feature") +
    theme(title = element_text(size = 9)) +
    facet_wrap(~ case_text + label_text + prob_text + r2_text,
               ncol = ncol, scales = "free")
  
}



plot_explanations_tq <- function(explanation) {
  
  data_transformed <- explanation %>%
    as.tibble() %>%
    dplyr::mutate(
      case    = as_factor(case),
      order_1 = rank(feature) 
    ) %>%
    dplyr::group_by(feature) %>%
    dplyr::mutate(
      order_2 = rank(feature_value)
    ) %>%
    dplyr::ungroup() %>%
    dplyr::mutate(
      order = order_1 * 1000 + order_2
    ) %>%
    dplyr::mutate(
      feature_desc = as.factor(feature_desc) %>% 
        fct_reorder(order, .desc =  T) 
    ) %>%
    dplyr::select(case, feature_desc, feature_weight, label)
  
  data_transformed %>%
    ggplot(aes(case, feature_desc)) +
    geom_tile(aes(fill = feature_weight)) +
    facet_wrap(~ label) +
    #theme_tq() +
    scale_fill_gradient2(low = palette_light()[[2]], mid = "white",
                         high = palette_light()[[1]]) +
    theme(
      panel.grid = element_blank(),
      legend.position = "right",
      axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)
    ) +
    labs(y = "Feature", x = "Case", 
         fill = glue("Feature
                         Weight"))
  
}


plot_hist_facet <- function(data, fct_reorder = FALSE, fct_rev = FALSE, 
                            bins = 10, fill = palette_light()[[3]], color = "white", ncol = 5, scale = "free") {
  print("Function Sanity Check: Plot Histogram that is Faceted")
  data_factored <- data %>%
    mutate_if(is.character, as.factor) %>%
    mutate_if(is.factor, as.numeric) %>%
    tidyr::gather(key = key, value = value, factor_key = TRUE) 
  
  if (fct_reorder) {
    data_factored <- data_factored %>%
      mutate(key = as.character(key) %>% as.factor())
  }
  
  if (fct_rev) {
    data_factored <- data_factored %>%
      mutate(key = fct_rev(key))
  }
  
  g <- data_factored %>%
    ggplot(aes(x = value, group = key)) +
    geom_histogram(bins = bins, fill = fill, color = color) +
    facet_wrap(~ key, ncol = ncol, scale = scale) #+ 
    #theme_tq()
  
  return(g)
  
}


get_cor <- function(data, target, use = "pairwise.complete.obs",
                    fct_reorder = FALSE, fct_rev = FALSE) {
  print("Function Sanity Check: Get Correlation of Features")
  feature_expr <- enquo(target)
  feature_name <- quo_name(feature_expr)
  
  data_cor <- data %>%
    mutate_if(is.character, as.factor) %>%
    mutate_if(is.factor, as.numeric) %>%
    cor(use = use) %>%
    as.tibble() %>%
    mutate(feature = names(.)) %>%
    select(feature, !! feature_expr) %>%
    filter(!(feature == feature_name)) %>%
    mutate_if(is.character, as_factor)
  
  if (fct_reorder) {
    data_cor <- data_cor %>% 
      mutate(feature = fct_reorder(feature, !! feature_expr)) %>%
      arrange(feature)
  }
  
  if (fct_rev) {
    data_cor <- data_cor %>% 
      mutate(feature = fct_rev(feature)) %>%
      arrange(feature)
  }
  
  return(data_cor)
  
}

plot_cor <- function(data, target, fct_reorder = FALSE, fct_rev = FALSE, 
                     include_lbl = TRUE, lbl_precision = 2, lbl_position = "outward",
                     size = 2, line_size = 1, vert_size = 1, 
                     color_pos = palette_light()[[1]], color_neg = palette_light()[[2]]) {
  print("Function Sanity Check: Plot Correlation of Features")
  feature_expr <- enquo(target)
  feature_name <- quo_name(feature_expr)
  
  data_cor <- data %>%
    get_cor(!! feature_expr, fct_reorder = fct_reorder, fct_rev = fct_rev) %>%
    mutate(feature_name_text = round(!! feature_expr, lbl_precision)) %>%
    mutate(Correlation = case_when(
      (!! feature_expr) >= 0 ~ "Positive",
      TRUE                   ~ "Negative") %>% as.factor())
  
  g <- data_cor %>%
    ggplot(aes_string(x = feature_name, y = "feature", group = "feature")) +
    geom_point(aes(color = Correlation), size = size) +
    geom_segment(aes(xend = 0, yend = feature, color = Correlation), size = line_size) +
    geom_vline(xintercept = 0, color = palette_light()[[1]], size = vert_size) +
    expand_limits(x = c(-1, 1)) +
    #theme_tq() +
    scale_color_manual(values = c(color_neg, color_pos)) 
  
  if (include_lbl) g <- g + geom_label(aes(label = feature_name_text), hjust = lbl_position)
  
  return(g)
  
}


# ggpairs: A lot of repetitive typing can be reduced 
plot_ggpairs <- function(data, color = NULL, density_alpha = 0.5) {
  print("Function Sanity Check: Plot ggpairs")
  color_expr <- enquo(color)
  
  if (rlang::quo_is_null(color_expr)) {
    
    g <- data %>%
      ggpairs(lower = "blank") 
    
  } else {
    
    color_name <- quo_name(color_expr)
    
    g <- data %>%
      ggpairs(mapping = aes_string(color = color_name), 
              lower = "blank", legend = 1,
              diag = list(continuous = wrap("densityDiag", 
                                            alpha = density_alpha))) +
      theme(legend.position = "bottom")
  }
  
  return(g)
  
}


###Genetic algorithm

custom_fitness <- function(vars, data_x, data_y, p_sampling)
{
  # speeding up things with sampling
  ix=get_sample(data_x, percentage_tr_rows = p_sampling)
  data_2=data_x[ix,]
  data_y_smp=data_y[ix]
  
  # keep only vars from current solution
  names=colnames(data_2)
  names_2=names[vars==1]
  # get the columns of the current solution
  data_sol=data_2[, names_2]
  
  # get the roc value from the created model
  roc_value=get_roc_metric(data_sol, data_y_smp, names_2)
  
  # get the total number of vars for the current selection
  q_vars=sum(vars)
  
  # time for your magic
  fitness_value=roc_value/q_vars
  
  return(fitness_value)
}

get_roc_metric <- function(data_tr_sample, target, best_vars) 
{
  # data_tr_sample=data_sol
  # target = target_var_s
  # best_vars=names_2
  
  fitControl <- caret::trainControl(method = "cv", 
                                    number = 3, 
                                    summaryFunction = twoClassSummary,
                                    classProbs = TRUE)
  
  data_model=select(data_tr_sample, one_of(best_vars))
  
  mtry = sqrt(ncol(data_model))
  tunegrid = expand.grid(.mtry=round(mtry))
  
  fit_model_1 = caret::train(x=data_model, 
                             y= target, 
                             method = "rf", 
                             trControl = fitControl,
                             metric = "ROC",
                             tuneGrid=tunegrid
  )
  
  metric=fit_model_1$results["ROC"][1,1]
  
  return(metric)
}




get_accuracy_metric <- function(data_tr_sample, target, best_vars) 
{
  print("Function Sanity Check: Check Accuracy Metrics")
  data_model=select(data_tr_sample, one_of(best_vars))
  
  fitControl <- trainControl(method = "cv", 
                             number = 3, 
                             summaryFunction = twoClassSummary)
  
  data_model=select(data_tr_sample, one_of(best_vars))
  
  mtry = sqrt(ncol(data_model))
  tunegrid = expand.grid(mtry=round(mtry))
  
  fit_model_1 = caret::train(x=data_model, 
                             y= target, 
                             method = "rf",
                             tuneGrid = tunegrid)
  
  
  
  metric=fit_model_1$results["Accuracy"][1,1]
  return(metric)
}  

# https://github.com/tobiolatunji/Readmission_Prediction/blob/master/diabetes_readmission.R
# pseudo R-squared for logistic regression model
logisticPseudoR2s <- function(LogModel) {
  print("Function Sanity Check: Calculate a logistic PseudoR2s")
  dev <- LogModel$deviance 
  nullDev <- LogModel$null.deviance 
  modelN <-  length(LogModel$fitted.values)
  R.l <-  1 -  dev / nullDev
  R.cs <- 1- exp ( -(nullDev - dev) / modelN)
  R.n <- R.cs / ( 1 - ( exp (-(nullDev / modelN))))
  cat("Pseudo R^2 for logistic regression\n")
  cat("Hosmer and Lemeshow R^2  ", round(R.l, 3), "\n")
  cat("Cox and Snell R^2        ", round(R.cs, 3), "\n")
  cat("Nagelkerke R^2           ", round(R.n, 3),    "\n")
}


#Variable Importance Function
tm_vip <- function (object, title, ...) {
  print("Function Sanity Check: Variable Importance Function")
  vip <- vip::vip(object = object, 
                  bar = TRUE,
                  horizontal = TRUE,
                  shape = 1,
                  color = "grey35",
                  fill = "grey35",
                  all_permutations = TRUE,
                  num_features = 10L,
                  alpha = 1) +
    ggtitle(title)
  return(vip)
}

tm_ggsave <- function (object, filename, ...){  #make sure the file name has quotation marks around it.  
  print("Function Sanity Check: Saving a ggplot image as a TIFF")
  ggplot2::ggsave(here::here("results", filename), object, device = "tiff", width = 10, height = 7, dpi = 200)
}


tm_print_save <- function (filename) {
  print("Function Sanity Check: Saving TIFF of what is in the viewer")
  dev.print(tiff, (here::here("results", filename)), compression = "lzw",width=2000, height=2000, bg="transparent", res = 200, units = "px" )
  dev.off()
}

tm_write2pdf <- function(object, filename) {  
  #pass filename and title with quotations
  print("Function Sanity Check: Creating Arsenal Table as a PDF")
  arsenal::write2pdf(object, (here::here("tables", (paste0(filename, ".pdf")))),
                     keep.md = TRUE,
                     quiet = TRUE) # passed to rmarkdown::render
}


tm_write2word <- function(object, filename) {  
  #pass filename and title with quotations
  print("Function Sanity Check: Creating Arsenal Table as a Word Document")
  arsenal::write2word(object, (here::here("tables", (paste0(filename, ".doc")))),
                      keep.md = TRUE,
                      quiet = TRUE) # passed to rmarkdown::render
}

tm_t_test <- function(variable){
  print("Function Sanity Test: t-test")
  output <- stats::t.test(y=variable[train$Match_Status == "Matched"],
                          x=variable[train$Match_Status == "Did not match"],
                          alternative = ("two.sided"),
                          paired = FALSE,
                          conf.level = 0.95,
                          var.equal = TRUE)
  
  print("X is group that did not match and Y is group that did match:")
  return(output)
}


tm_chi_square_test <- function (variable) {
  print("Function Sanity Test: chi-square test")
  chisq <- stats::chisq.test(variable, train$Match_Status, correct = FALSE)
  return(chisq)
}
```


```{r directory paths and packrat settings, include=FALSE}
#Helpful, https://www.kaggle.com/pjmcintyre/titanic-first-kernel/code
# https://bradleyboehmke.github.io/HOML/

cat("\014")  #Clear console
# I want to use packrate to make the project more: isolated, portable and reproducible.  Please see packrat/packrat.lock for a list of the precise packages used and their versions.  Be sure to check in the .Rprofile, packrat.lock files, and everything under packrat/src/. 
#packrat::packrat_mode(on = TRUE)
#packrat::status()
#packrat::clean()
#packrat::restore()
#packrat::snapshot(infer.dependencies = FALSE, snapshot.sources = FALSE, ignore.stale = TRUE)  #Run each time a new library is installed.

#packrat::bundle(include.lib = TRUE, include.src = TRUE, omit.cran.src = TRUE)  #Use this for portability
#Bundle is stored in packrat/bundles/***.tar.gz

#options(tinytex.verbose = FALSE)
library(knitr)
```


```{css echo = FALSE}
#Taken from the Pudding.cool
pre code, pre, code {
  white-space: pre !important;
  overflow-y: scroll !important;
  max-height: 25vh !important;
}
```

Package installation, data download from Dropbox.com, and functions written for this project are all loaded in a separate "Additional_functions_nomogram.R" file.
```{r, echo=TRUE, include = FALSE}
here::set_here()  #set_here() creates an empty file named .here, by default in the current directory.Sets root.  
here::here()
#May need to run this file line-by-line (CRTL+Enter) by hand.  

#source(file=(here::here("Code", "Additional_functions_nomogram.R")), echo=TRUE, verbose=TRUE)
all_data <- readr::read_csv("~/Dropbox/Nomogram/nomogram/data/All_ERAS_data_merged_output_2_1_2020.csv")

library(magrittr)
all_data <- all_data %>%
  dplyr::select(-Applicant_Name)
conflicts()
```

The first few rows of the data loaded are given below:
```{r}
library(magrittr)
head(all_data) %>% knitr::kable(format = "pandoc", caption = "Example observations (rows) and the features (columns)")
```


# Ingest Data:  Load and Tidy the Data
`all_data` is a dataframe of the independent and the dependent variables for review. Each variable is contained in a column, and each row represents a single unique medical student. If students applied in more than one year the most contemporary data was used.
```{r Download cleaned data from Dropbox, echo=TRUE, include=FALSE, cache=FALSE}
all_data
dim(all_data)
dim(all_data)
data.table::data.table(all_data)
funModeling::freq(data=all_data, plot = FALSE, na.rm = FALSE)
dplyr::glimpse(all_data)

summarytools::view(summarytools::dfSummary(x = all_data, justify = "l", style = "multiline", varnumbers = FALSE, valid.col = FALSE, tmp.img.dir = "./img", max.distinct.values = 5))

# orginal response distribution
tmp <- table(all_data$Match_Status)
match_rate <- (tmp[[1]]/(tmp[[2]] + tmp[[1]]))*100
match_rate
rm(tmp)
```
We can see that these data have `r nrow(all_data)` observations of `r ncol(all_data)` features, and thatabout `r round(match_rate, digits = 1)` percent of medical students applying to OB/GYN residency matched.   Let’s create a few plots to get a sense of the data. Remember, the goal here will be to predict whether a given medical student will match into OB/GYN residency, based on the variables listed in the codebook.

# Description of the Data
* A summary of the variables are listed below:
1. Eleven of the variables were a factor.  All factors had two levels except for Alpha_Omega_Alpha had three levels.  The target variable is `all_data$Match_Status`.  
2. Eight of the variables were integers. 

```{r structure of data, include=TRUE, echo=TRUE, out.width="75%"}
# examine the structure of the initial data frame
all_data$Count_of_Peer_Reviewed_Journal_Articles_Abstracts <- as.numeric(all_data$Count_of_Peer_Reviewed_Journal_Articles_Abstracts)
all_data$Age <- as.numeric(all_data$Age)
all_data$Count_of_Poster_Presentation <- as.numeric(all_data$Count_of_Poster_Presentation)
all_data$USMLE_Step_1_Score <- as.numeric(all_data$USMLE_Step_1_Score)
all_data$Count_of_Oral_Presentation <- as.numeric(all_data$Count_of_Oral_Presentation)
all_data$Count_of_Peer_Reviewed_Journal_Articles_Abstracts_Other_than_Published <- as.numeric(all_data$Count_of_Peer_Reviewed_Journal_Articles_Abstracts_Other_than_Published)
all_data$Count_of_Peer_Reviewed_Book_Chapter <- as.numeric(all_data$Count_of_Peer_Reviewed_Book_Chapter)
all_data$Count_of_Non_Peer_Reviewed_Online_Publication <- as.numeric(all_data$Count_of_Non_Peer_Reviewed_Online_Publication)
all_data$USMLE_Step_2_CK_Score <- as.numeric(all_data$USMLE_Step_2_CK_Score)

inspectdf::inspect_types(all_data) %>% inspectdf::show_plot()

all_data <- all_data %>% dplyr::select(-Medical_School_of_Graduation)
```

```{r}
#https://github.com/manojmukkamala/DiabeticPatientsReadmission/blob/master/Project_V4.R
#Just writing the names of all the variables under one term to avoid re-writing when we apply model multiple times

#"Malpractice_Cases_Pending", Removed because this is due to the fact that all people had 0 cases

drivers <- c("ACLS",
                                                                     "Age",
                                                       "Alpha_Omega_Alpha",
                                                         # "Applicant_Name",
                                                                     "BLS",
                                                             "Citizenship",
                           "Count_of_Non_Peer_Reviewed_Online_Publication",
                                              "Count_of_Oral_Presentation",
                                                 "Count_of_Other_Articles",
                                    "Count_of_Peer_Reviewed_Book_Chapter",
                      "Count_of_Peer_Reviewed_Journal_Articles_Abstracts",
 "Count_of_Peer_Reviewed_Journal_Articles_Abstracts_Other_than_Published",
                              "Count_of_Peer_Reviewed_Online_Publication",
                                           "Count_of_Poster_Presentation",
                                          "Count_of_Scientific_Monograph",
                                                          "Couples_Match",
                                                                 "Gender",
                                                           "Match_Status",
                                                         "Medical_Degree",
                              "Medical_Education_or_Training_Interrupted",
                                              "Medical_Licensure_Problem",
                                            "Military_Service_Obligation",
                                                 "Misdemeanor_Conviction",
                                                            "NIH_dollars",
                                                                   "PALS",
                                                        "Sigma_Sigma_Phi",
                                                 "Type_of_medical_school",
                                               "US_or_Canadian_Applicant",
                                                     "USMLE_Step_1_Score",
                                                  "USMLE_Step_2_CK_Score",
                                                "Visa_Sponsorship_Needed",
                                                        "white_non_white")

#Writing the name of dependent variable seperately
dependentVar <- "Match_Status"

#Bringing all the column names under one term
formula <- paste(dependentVar, "~", paste(drivers, collapse = " + "))
formula
```

```{r Describe data, include=FALSE}
Hmisc::describe(all_data)
```
A nice data summary is available from the `skim` package.   
```{r,include=TRUE}
skimr::skim(all_data)
```

# Evaluate for missing data in multiple manners
```{r,EDA, results="asis", echo=TRUE, include=TRUE, out.width="50%"}
#plot_str(all_data) #COOL BUT USELESS HERE
DataExplorer::plot_missing(all_data)
DataExplorer::plot_intro(all_data)
```

The new data set in `all_data`, includes `r nrow(all_data)` rows and `r ncol(all_data)` columns.  The `r (english::words(nrow(all_data)))` applicants are missing `r (english::words(sum(is.na(all_data))))` values.    

Shows four different ways to check for missingness in the data 
```{r, four ways to look for missingness, include=FALSE, out.width="50%"}
tm_print_save <- function (filename) {
  print("Function Sanity Check: Saving TIFF of what is in the viewer")
  dev.print(tiff, (here::here("results", filename)), compression = "lzw",width=2000, height=2000, bg="transparent", res = 200, units = "px" )
  dev.off()
}

#Cool but a little overkill with three ways for checking if we have missing data.  
sum(is.na(all_data))
all_data <- na.omit(all_data)
colSums(is.na(all_data))
purrr::map_df(all_data, ~ sum(is.na(.)))

naniar::gg_miss_var(all_data)
tm_print_save(filename = "na_pattern.tiff")

na_pattern <- Hmisc::na.pattern(all_data)
na_pattern

sum(is.na(all_data))
```




# Exploratory data analysis
After the data check was completed, an exploratory data analysis (EDA) was conducted to look for interesting relationships among the variables. Histograms were used to visualize distributions among predictors. Since the outcome of Matching is a classification problem, relationships between predictors and the dichotomous outcome were also performed. 

Description of `all_data$Match_Status` variable.  
```{r data check, include=TRUE, out.width="50%"}
#Added function for Rmarkdown
tm_ggsave <- function (object, filename, ...){  #make sure the file name has quotation marks around it.  
  print("Function Sanity Check: Saving a ggplot image as a TIFF")
  ggplot2::ggsave(here::here("results", filename), object, device = "tiff", width = 10, height = 7, dpi = 200)
}

# 
# Hmisc::describe(as.factor(all_data$Match_Status))
# whomatched <- 
#   ggplot2::ggplot(all_data[!is.na(all_data$Match_Status),], aes(x = Match_Status, fill = Match_Status)) +
#   ggplot2::geom_bar(stat='count') +
#   ggplot2::labs(x = 'How many applicants matched into OBGYN?') +
#         ggplot2::geom_label(stat='count',aes(label=..count..), size=7) +
#         ggplot2::theme_grey(base_size = 18)
# whomatched
# 
# tm_ggsave(object = whomatched, filename = "whomatched.tiff")
```

# Data Description and *Univariate* analysis of variables. 
Categorical and numerical variable plots:
```{r DataExplorer, results='asis', echo=TRUE, include=TRUE, align = 'left', cache=FALSE, out.width="75%"}
#General Data Description
inspect_cat_plot <- inspectdf::inspect_cat(all_data) %>% inspectdf::show_plot()  #Please use `cols = c(data)` is the error message I get here.  But it still runs.  
inspect_cat_plot
tm_ggsave(object = inspect_cat_plot, filename = "inspect_cat_plot.tiff")

plot_histogram_plot <- DataExplorer::plot_histogram(all_data, nrow = 2L, ncol = 2L)  
plot_histogram_plot

DataExplorer::plot_bar(all_data, nrow = 2L, ncol = 2L)  #Not useful whatsoever.  

#Univariate of boxplots
inspect_num_plot <- inspectdf::inspect_num(all_data) %>% inspectdf::show_plot()  
inspect_num_plot

tm_ggsave(inspect_num_plot, "inspect_num_plot.tiff")
```

```{r, include=TRUE, echo=TRUE, include=TRUE, align = 'left', cache=FALSE, out.width="75%"}
#EDA,  https://ryjohnson09.netlify.com/post/caret-and-tidymodels/
# Create vector of predictors and subtract the last column with the target variable
#Function for RMarkdown
#Tidymodels feature plots

expl <- names(all_data)[-32]  #[-19]

# Loop vector with map
#expl_plots_box <- purrr::map(expl, ~box_fun_plot(data = all_data, x = "Match_Status", y = .x) )
#plot_grid_plot <- cowplot::plot_grid(plotlist = expl_plots_box)
#plot_grid_plot

#tm_ggsave(plot_grid_plot, "plot_grid_plot.tiff")

# Loop vector with map
#expl_plots_density <- purrr::map(expl, ~density_fun_plot(data = all_data, x = "Match_Status", y = .x) )
# plot_grid_plot_density <- cowplot::plot_grid(plotlist = expl_plots_density)
# plot_grid_plot_density

#tm_ggsave(plot_grid_plot_density, "plot_grid_plot_density.tiff")
```


```{r funModeling2, echo=TRUE, message=FALSE, warning=TRUE, include=FALSE}
create_plot_num <- 
  function(data) {
    print("Function Sanity Check: Plot Numeric Features")
    funModeling::plot_num(data, path_out = results_folder)
  } 

#create_plot_num_plot <- create_plot_num(all_data)  
#create_plot_num_plot

#tm_ggsave(create_plot_num_plot, "create_plot_num_plot.tiff")
```

```{r funModeling1, echo=TRUE, message=FALSE, warning=TRUE, results='asis', include=FALSE}
df_status_output <- funModeling::df_status(all_data)
#desc_groups(data=all_data, group_var="Match_Status")  #Breaks the knitr for some reason
df_status_output
readr::write_csv(df_status_output, (here::here("results", "df_status_output.csv")))
```

```{r funModeling3, echo=TRUE, message=FALSE, warning=TRUE, results='asis', include=FALSE}
#Summary stats of the numerical data showing means, medians, skew
create_profiling_num_output <- create_profiling_num(all_data)   
all_data %>% mosaic::inspect()  #another good option
readr::write_csv(create_profiling_num_output, (here::here("results", "create_profiling_num_output.csv")))
```


# Cross plots of predictors by outcome
```{r funModeling4, echo=TRUE, message=FALSE, warning=TRUE, include=TRUE, out.width="75%"}
#Not working with markdown

#DataExplorer::plot_boxplot(all_data, by = "Match_Status", nrow = 2L, ncol = 2L)
#Shows the variable frequency charted by matching status
#create_plot_cross_plot(all_data)   
```


# Table: Applicant Descriptive Variables by Matched or Did Not Match from 2015 to 2018
```{r, echo=TRUE, warning=FALSE, message=FALSE, include=TRUE, results="asis"}
#Added for Rmarkdown, NOT WORKING NOW!!!
# Draws a nice table one plot

# Draws a nice table one plot
# tm_arsenal_table = function(df, by){
#   print("Function Sanity Check: Create Arsenal Table using arsenal package")
#   table_variable_within_function <- arsenal::tableby(by ~ .,
#                  data=df, control = tableby.control(test = TRUE,
#                                                                 total = F,
#                                                                 digits = 1L,
#                                                                 digits.p = 2L,
#                                                                 digits.count = 0L,
#                                                                 numeric.simplify = F,
#                                                                 numeric.stats =
#                                                                   c("median",
#                                                                     "q1q3"),
#                                                                 cat.stats =
#                                                                   c("Nmiss",
#                                                                     "countpct"),
#                                                                 stats.labels = list(Nmiss = "N Missing",
#                                                                                     Nmiss2 ="N Missing",
#                                                                                     meansd = "Mean (SD)",
#                                                                                     medianrange = "Median (Range)",
#                                                                                     median ="Median",
#                                                                                     medianq1q3 = "Median (Q1, Q3)",
#                                                                                     q1q3 = "Q1, Q3",
#                                                                                     iqr = "IQR",
#                                                                                     range = "Range",
#                                                                                     countpct = "Count (Pct)",
#                                                                                     Nevents = "Events",
#                                                                                     medSurv ="Median Survival",
#                                                                                     medTime = "Median Follow-Up")))
#   final <- summary(table_variable_within_function,
#           text=T,
#           title = 'Table: Applicant Descriptive Variables by Matched or Did Not Match from 2015 to 2018',
#           labelTranslations = mylabels, #Seen in additional functions file
#           pfootnote=TRUE)
#   return(final)
# }
# 
# tm_arsenal_table_output <- tm_arsenal_table(df = all_data, by = all_data$Match_Status)
# tm_arsenal_table_output
# 
# tm_write2word(tm_arsenal_table_output, "tm_arsenal_table_output1")
# tm_write2pdf(tm_arsenal_table_output, "tm_arsenal_table_output1")
```

```{r}
readr::write_csv(all_data, "~/Dropbox/Nomogram/nomogram/all_data_end_of_EDA.csv")
file.exists("~/Dropbox/Nomogram/nomogram/all_data_end_of_EDA.csv")
```




